ternary_hyper2

### 2022-11-21 inst/ternaryplot_hyper2.Rmd
use the icons dataset in a ternary plot (issue #187)

@@

>>>>

## The `chess` dataset

@@

## The `icons` dataset

Consider the `icons` likelihood function:

```{r showicons}
icons
```

We can sample from this object and plot it in different ways:

```{r samplefromicons,cache=TRUE}
n <- 10000
x <- rp(n,icons)
x[sample(n,5),]
```

```{r, iconsmatplot}
matplot(x,type="l",lty=1)
legend("topright",col=1:6,lty=1,legend=pnames(icons))
```

```{r, selectjustbigones}
wanted <- c(1,3) # NB,PB
xx <- cbind(x[,wanted],fillup=rowSums(x[,-wanted]))
TernaryPlot(atip="NB",btip="PB",ctip="other")
TernaryPoints(xx,cex=0.5)
```
